Sustainable behaviour

### 2020-11-27 03-comportements.Rmd
adding info on behaivour

>>>>

# On pro-environmental behaviours

- @Yuriev2020 identified nine systematic literature reviews on pro-environmental behaviors  (Li et al., 2019; Lo et al., 2012; Koop et al., 2019; Staddon et al., 2016; Varotto and Spagnolli, 2017; Inoue and Alfaro-Barrantes, 2015; Francoeur et al., 2019; Norton et al., 2015; Yuriev et al., 2018). 
These are the only existing systematic literature reviews from the last 10 years that covered various individual environmental actions. Having
